Causal graph analysis of COVID-19 observational data in German districts reveals effects of mobility, awareness, and temperature

### 2021-03-01 manuscript/v4_medrxiv_revision/manuscript.Rmd
add new folders for revision, test latexdiff
use latexdiffr

>>>>

```{r rundifflatex, message=FALSE, warning=FALSE, include=FALSE}
# careful, it's always one version behind
library(latexdiffr)
latexdiff("../v2_medrxiv/manuscript.tex", "manuscript.tex", "latexdiffrRmd")
# system("latexdiff ../v2_medrxiv/manuscript.tex manuscript.tex > diffRmd.tex")
# tinytex::pdflatex("diffRmd.tex")
```
